Evaluating FAIR Digital Object as a distributed object system

### 2023-01-30 latex/main.tex
Updates from Overleaf
table tidy

%% Definitions needed for pandoc's silly output

\usepackage{hyperref}
\hypersetup{
  pdflang={en-GB},
  hidelinks
}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage{longtable,booktabs,array}

%% CSL definitions for pandoc's generated references
%% https://github.com/jgm/pandoc/blob/2.19.2/data/templates/default.latex#L302
\newlength{\cslhangindent}
\setlength{\cslhangindent}{0.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{2em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

%% END

%% STTYX2Fonts for lualatex
% https://www.overleaf.com/learn/latex/Articles%2FOpenType-based_math_typesetting%3A_An_introduction_to_the_STIX2_OpenType_fonts
\usepackage{amsmath}
%\usepackage{hyperref}
\usepackage{fontspec}
\usepackage{unicode-math}
%\usepackage{hologo}
%\usepackage{graphicx}
\setmathfont{STIX2Math}[
Extension={.otf},
Path=./STIX2fonts/,
Scale=1]
\setmainfont{STIX2Text}[
Extension={.otf},
Path=./STIX2fonts/,
UprightFont={*-Regular},
BoldFont={*-Bold},
ItalicFont={*-Italic},
BoldItalicFont={*-BoldItalic}]
%% END

%%%% END pandoc defs
%%% Additional packages/definitions
\usepackage{citation-style-language}
\cslsetup{
style = peerj
}
\addbibresource{bibliography.json}

@@

The FAIR principles \cite{6DjakjNS} encourage sharing of scientific data with machine-readable metadata and the use of interoperable formats, and are being adapted by a wide range of research infrastructures. They have been widely recognised by the research community and policy makers as a goal to strive for. In particular, the European Open Science Cloud (\href{https://www.eosc.eu/}{EOSC}) has promoted adaptation of FAIR data sharing of data resources across electronic research infrastructures \cite{u8Cy0psL}. The EOSC Interoperability Framework \cite{aCye3KpE} puts particular emphasis on how interoperability can be achieved technically, semantically, organisationally, and legally -- laying out a vision of how data, publication, software and services can work together to form an ecosystem of rich digital objects.

@@

%%\bibliography{sample}
\printbibliography

>>>>

%% Note: This latex project needs lualatex from texlive 2022 or later.

%% Definitions needed for pandoc's silly output
\usepackage{hyperref}
\hypersetup{
  pdflang={en-GB},
  hidelinks
}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\usepackage{longtable,booktabs,array}
%% END pandoc

%%%% END pandoc defs
%%% Additional packages/definitions
%\usepackage{citation-style-language}
%\cslsetup{
%style = peerj
%}
%\addbibresource{bibliography.json}

@@

The FAIR principles \cite{wilkinson_fair_2016} and \cite{working_group_doip_2022} and \cite{noauthor_info_nodate} encourage sharing of scientific data with machine-readable metadata and the use of interoperable formats, and are being adapted by a wide range of research infrastructures. They have been widely recognised by the research community and policy makers as a goal to strive for. In particular, the European Open Science Cloud (\href{https://www.eosc.eu/}{EOSC}) has promoted adaptation of FAIR data sharing of data resources across electronic research infrastructures \cite{u8Cy0psL}. The EOSC Interoperability Framework \cite{aCye3KpE} puts particular emphasis on how interoperability can be achieved technically, semantically, organisationally, and legally -- laying out a vision of how data, publication, software and services can work together to form an ecosystem of rich digital objects.

@@

\bibliography{bibliography}
%\printbibliography

### 2023-01-30 latex/table1.tex
table tidy

\textbf{Symbiotic}: \emph{to what extent multiple applications can agree to interact/align/collaborate/cooperate} & The purpose of FDO is to enable federated machine actionable digital objects for scholarly purposes, in practice this also requires agreement of or compatibility between FDO types. FDO encourages research communities to develop common type registries to be shared across instances. In current DOIP practice, each service have their own types, attributes and operations. The wider symbiosis is consistent use of PIDs. & The Web is loosely coupled and encourages collaboration and linking by URL. In practice, REST APIs \cite{174AwcFUL} end up being mandated centrally by dominant (often commercial) providers \cite{11VxBOeZy}, which clients are required to use as-is with special code per service. Use of Linked Data enables common tooling and semantic mapping across differences. \\

>>>>

\textbf{Symbiotic}: \emph{to what extent multiple applications can agree to interact, align, collaborate or cooperate} & The purpose of FDO is to enable federated machine actionable digital objects for scholarly purposes, in practice this also requires agreement of or compatibility between FDO types. FDO encourages research communities to develop common type registries to be shared across instances. In current DOIP practice, each service have their own types, attributes and operations. The wider symbiosis is consistent use of PIDs. & The Web is loosely coupled and encourages collaboration and linking by URL. In practice, REST APIs \cite{174AwcFUL} end up being mandated centrally by dominant (often commercial) providers \cite{11VxBOeZy}, which clients are required to use as-is with special code per service. Use of Linked Data enables common tooling and semantic mapping across differences. \\
